### 2023-11-20 main.tex
partial

@@

	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]

@@

		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$. In the last equality we have summed over all possible $\sigma\in \Omega^{'}$. From Section \ref{correlation-section} we recall that the components of $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state. Thus, we have that  
			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]

@@

				indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
			\end{comment}
			Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
			\begin{flushright}
				$\square$
			\end{flushright}
		\begin{comment}
			\begin{remark}[Non-equilibrium steady state using exact correlations]
			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
				\begin{align}
					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
				\end{align}
				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that 
				\begin{equation}
				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
				\end{equation}
			where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
				\end{remark}
		\end{comment}
				\begin{comment}
					where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
					\begin{equation}
						\begin{cases}
							\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
							\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
						\end{cases}
					\end{equation}
					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
					\begin{equation}
						\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
					\end{equation}
					Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
					\begin{equation}
						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
					\end{equation}
				\end{comment}

>>>>

\begin{remark}[Interpretation the elements $\Psi^{'}(\bm{\tau})$]
	For any given $\bm{\tau}\in \Omega^{'}$ we have that 
	\begin{equation}\label{interpretation-PsiP}
		\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]
Indeed, arguing as in the previous proof, we have that
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\sigma\in \Omega}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle
We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it in a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by
	\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
	\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$. Therefore, we have
	\Psi^{'}(\bm{\tau})=&\sum_{\sigma\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle
We observe that for any $x\in \{1,\ldots,L\}$ the duality function \eqref{ElementsDualityMatrixChain_1} is
	d_{x}(\sigma_{x},\xi^{x}(\bm{\tau}))=\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
 Therefore, equation \eqref{interpretation-PsiP} follows. 

@@

	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{1-\delta_{\tau_{x},N}}\right]

@@

		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$. In the last equality we have summed over all possible $\sigma\in \Omega^{'}$. From Section \ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}. Thus, we have that  
			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{1-\delta_{\tau_{x},N}}\right]

@@

				indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
			Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
Formula \eqref{SteadyState-coeff-implicit} can be also obtained without inverting the matrix $S_{1}$, but just using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
				\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\mu\left(\sigma_{1}=\tau_{1},\ldots,\sigma_{L}=\tau_{L}\right)=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\nonumber\\
				=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\right]\nonumber\\
				=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}\right)\right)\right]
				%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
			%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
			%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
				%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
		where in the up to last line we exploited the fact that 
		\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}
		Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$	we retrieve \eqref{SteadyState-coeff-implicit}.
			\begin{remark}[Non-equilibrium steady state using exact correlations]
			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that 
				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
					where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
							\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
							\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
						\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
					Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
